Global patterns of forest autotrophic carbon fluxes

### 2020-05-04 manuscript/manuscript draft.Rmd
reviewing refs/ working on discusion
#69 , #43

**See [issue #70](https://github.com/forc-db/Global_Productivity/issues/70), and potentially rework paragraph. **
We show that, with the exception of some differences in MAT-MAP interactions (Fig. 3), FACF are broadly consistent in their responses to climate drivers on the global scale, with no pronounced trends in C allocation among the variable pairs tested (Figs. 2, S3). Although variation in allocation has been observed along gradients of elevation [@moser_elevation_2011] and water availability [@newman_above-_2006]--along with non-climatic axes of stand age [@litton_carbon_2007], nutrient availability [@litton_carbon_2007; @gill_belowground_2016], and forest structure [@taylor_greater_2019]--little variation in relation to climate is apparent at the global scale. Our conclusion, then, is that hypothesized gradients in allocation along global climate gradients cannot currently be supported for mature forests, although data quantity and standardization is currently insufficent to rule out the possibility that such trends exist. There have been suggestions that tropical forests tend to have low carbon use efficiency ($CUE$= $NPP$/$GPP$=($GPP$-$R_{auto}$/$GPP$), which are based on observations of low $CUE$ in old-growth tropical forests relative to (mostly younger) extratropical forests [@delucia_forest_2007; @malhi_productivity_2012; @anderson-teixeira_carbon_2016], but our analysis suggests that these low values might more appropriately be attributed to the fact that these forests are old than to their tropical climate. Indeed, $CUE$ is known to decline with forest age [@delucia_forest_2007; @collalti_is_2019], but appears to be roughly independent of $GPP$ [@litton_carbon_2007]. Among our sites with relevant data, there are no signficant trends in allocation of $GPP$ to $NPP$ or of $NPP$ to $ANPP_{woody-stem}$ across gradients of latitude or climate (Fig. S3). Additional measurements with careful methodological standardization across a consistent set of mature forest sites will be necessary to determine whether any climate-driven gradients in allocation exist at the global scale.

@@

- consistent with [@hofhansl_new_2015] (**verify**) , we found a slight tendency for warmer sites to have higher aboveground allocation

>>>>

**See [issue #70](https://github.com/forc-db/Global_Productivity/issues/70), and potentially rework paragraph. **
We show that, with the exception of some differences in MAT-MAP interactions (Fig. 3), FACF are broadly consistent in their responses to climate drivers on the global scale, with no pronounced trends in C allocation among the variable pairs tested (Figs. 2, S3) . Although variation in allocation has been observed along gradients of elevation [@moser_elevation_2011] and water availability [@newman_above-_2006]--along with non-climatic axes of stand age [@litton_carbon_2007], nutrient availability [@litton_carbon_2007; @gill_belowground_2016], and forest structure [@taylor_greater_2019]--little variation in relation to climate is apparent at the global scale. Our conclusion, then, is that hypothesized gradients in allocation along global climate gradients cannot currently be supported for mature forests, although data quantity and standardization is currently insufficent to rule out the possibility that such trends exist. There have been suggestions that tropical forests tend to have low carbon use efficiency ($CUE$= $NPP$/$GPP$=($GPP$-$R_{auto}$/$GPP$), which are based on observations of low $CUE$ in old-growth tropical forests relative to (mostly younger) extratropical forests [@delucia_forest_2007; @malhi_productivity_2012; @anderson-teixeira_carbon_2016], but our analysis suggests that these low values might more appropriately be attributed to the fact that these forests are old than to their tropical climate. Indeed, $CUE$ is known to decline with forest age [@delucia_forest_2007; @collalti_is_2019], but appears to be roughly independent of $GPP$ [@litton_carbon_2007]. Among our sites with relevant data, there are no signficant trends in allocation of $GPP$ to $NPP$ or of $NPP$ to $ANPP_{woody-stem}$ across gradients of latitude or climate (Fig. S3). Additional measurements with careful methodological standardization across a consistent set of mature forest sites will be necessary to determine whether any climate-driven gradients in allocation exist at the global scale.

*reworking the above paragraph:*
We show that FACF are broadly consistent in their responses to climate drivers on the global scale, with at most modest trends in C allocation among the variable pairs tested (Figs. 2, S3). 
This parallels the observation that C allocation across multiple FACF varies little with respect to climate along a tropical elevational gradient [@malhi_variation_2017], 
but contrasts with observed variation in allocation along gradients of elevation [@moser_elevation_2011] and water availability [@newman_above-_2006]
- @gill_belowground_2016 ?
- (others in list below?)
Several trends in allocation--or lack thereof--warrant discussion.
1. CUE
2. We found a slight tendency for warmer sites to have higher aboveground allocation (Fig. S3). This is consistent with:
- [@hofhansl_new_2015] (**verify**) 
- Chen et al. 2019 (doi: 10.1111/ele.13193) - find lower partitioning belowground at higher productivity (fine root NPP scales against ANPP_foliage with a slope of ~ 0.8)
- @gill_belowground_2016
- @litton_carbon_2007 - (verify)

@@
